Risk Perceptions for Wearable Devices

### 2015-03-06 tex-inputs/methodology.tex
Capitalize proper nouns (names of products)

\section{Methodology}
To obtain a comprehensive list of possible risks that wearable devices might present in the future, we examined the sensors, capabilities, permissions, and applications of the most popular wearable devices on the market at the time of this study. At the time of this study, August 2014, the most popular wearable devices included the fitbit fitness tracker which performs continuously monitors heartbeat, steps taken, and sleep patterns \cite{6_fitbit_2014, 7_time_2014}, the pebble smartwatch which can take pictures, send texts, show notifications from online, and push notifications to services \cite{pebble_smartwatch_2014, 9_verge_2014, 10_readwrite_2014}, and google glass \cite{11_wikipedia_2015, 12_turi_2014}. These wearable devices, along with other comparable wearable devices on the market, were researched as inspiration for the survey questions.

>>>>

\section{Methodology}
To obtain a comprehensive list of possible risks that wearable devices might present in the future, we examined the sensors, capabilities, permissions, and applications of the most popular wearable devices on the market at the time of this study. At the time of this study, August 2014, the most popular wearable devices included the Fitbit fitness tracker which performs continuously monitors heartbeat, steps taken, and sleep patterns \cite{6_fitbit_2014, 7_time_2014}, the Pebble smartwatch which can take pictures, send texts, show notifications from online, and push notifications to services \cite{pebble_smartwatch_2014, 9_verge_2014, 10_readwrite_2014}, and Google Glass \cite{11_wikipedia_2015, 12_turi_2014}. We used these wearable devices, along with other comparable wearable devices on the market, as inspiration for the survey questions.
